Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-13 SDSS-2023/testing-charts-accuracy.qmd
move packages to preamble

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
short-title: Testing charts in surveys # running title
author:
  - first: Kiegan                 # first name
    first-init: K.              # initial of first name
    last: Rice                  # last name
    marker: 1               # identifier for the affiliation
    footnote-id: 1              # optional identifier for the footnote
    email: foo@bar.com          # optional email address
  - first: Heike
    first-init: H.
    last: Hofmann
    marker: 2
  - first: Nola
    first-init: N.
    last: duToit
    marker: 1
  - first: Edward
    first-init: E.
    last: Mulrow
    marker: 1
footnote:
  - content: Corresponding author
    type: corresp               # set type for the corresponding author
    id: 1
affiliation:
  - institution: National Opinion Research Center (NORC)
    country: United States
    marker: 1
  - institution: Iowa State University
    department: Statistics
    country: United States
    marker: 2
bibliography: references.bib
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
format:
  pdf:
    documentclass: jds
    fig-width: 6
    fig-asp: 0.618
    fig-align: center
    include-in-header: 
      - text: |
          \usepackage{amsfonts,amsmath,amssymb,amsthm}
          \usepackage{booktabs}
          \usepackage{graphicx}
          \usepackage{longtable}
          \usepackage{hyperref}
      - file: edits.tex
    cite-method: natbib
    keep-tex: true
    keep-md: true
---

\hh{hello?}

\kr{Kiegan, this is your editing color :) - you can choose a different color in edits.tex}

@@

@@

\hh{We can combine responses across samples into one combined dataset, but we need to adjust weights accordingly so that each sample is weighted equally in the model [@omuircheartaighCombiningSamplesVs2002].}

@@

\hh{Using the AmeriSpeak survey tool, a total of 1902 participants were exposed to two barcharts each, as shown in \autoref{tbl-tasks-12}.}

>>>>

---
title: "Testing Charts: viewer's perceptual accuracy in surveys"
short-title: Testing charts in surveys # running title
author:
  - first: Kiegan                 # first name
    first-init: K.              # initial of first name
    last: Rice                  # last name
    marker: 1               # identifier for the affiliation
    footnote-id: 1              # optional identifier for the footnote
    email: foo@bar.com          # optional email address
  - first: Heike
    first-init: H.
    last: Hofmann
    marker: 2
  - first: Nola
    first-init: N.
    last: duToit
    marker: 1
  - first: Edward
    first-init: E.
    last: Mulrow
    marker: 1
footnote:
  - content: Corresponding author
    type: corresp               # set type for the corresponding author
    id: 1
affiliation:
  - institution: National Opinion Research Center (NORC)
    country: United States
    marker: 1
  - institution: Iowa State University
    department: Statistics
    country: United States
    marker: 2
bibliography: references.bib
abstract: "The use of visuals is a key component in scientific communication, and decisions about the design of a data visualization should be informed by what design elements best support the audience's ability to perceive and understand the components of the data visualization. We build on the foundations of Cleveland and McGill's work in graphical perception, employing a large, nationally-representative, probability-based panel of survey respondents to test perception in statistical charts. Our findings provide actionable guidance for data visualization practitioners to employ in their work."
keywords: 'list, keywords, here, 3-6, are, fine'
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
  \usepackage{booktabs}
  \usepackage{graphicx}
  \newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
  \newcommand{\kr}[1]{{\textcolor{teal}{#1}}}
  \setlength{\parindent}{0pt}
format:
  pdf: default
documentclass: jds
---

<!-- \hh{hello?} -->
<!-- fig-width: 6.5 -->
<!-- fig-height: 4.5 -->
<!-- template: template-jdsart.cls.tex -->

<!-- \kr{Kiegan, this is your editing color :) - you can choose a different color above} -->

@@

knitr::opts_chunk$set(
  jds.rmd::pdf_article()$knitr
)

@@

We can combine responses across samples into one combined dataset, but we need to adjust weights accordingly so that each sample is weighted equally in the model [@omuircheartaighCombiningSamplesVs2002].

@@

Using the AmeriSpeak survey tool, a total of 1902 participants were exposed to two barcharts each, as shown in \autoref{tbl-tasks-12}.
